Importance sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-02-17 draft_p2.tex
Adds figures ecoulement_typique and PDF_AVG
Updates caption for ecoulement typique

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{typical_drag_signal/typical_drag_signal.png}
  \caption{Typical temporal evolution of the drag acting on the square cylinder pictured in figure~\ref{fig:computational_domain}. The correlation time $\tau_c$ is defined further in this text and correspond to the typical fluctuation timescale of the drag.}
  \label{fig:typical_drag_signal}
\end{figure}

@@

% Malgré les limitations, c'est toujours mieux
% qu'un échantillonnage direct
Unsurprisingly, sampling larger fluctuations requires a larger population size, and therefore a larger computational cost.
Even though, table~\ref{tbl:nbTraj_tbl} shows that the \ac{gktl} algorithm is able to sample trajectories corresponding to values of the time-averaged drag that could
not be sampled through a direct sampling with equal computational cost.
Table~\ref{tbl:nbTraj_tbl} displays the number of trajectories that correspond to a time-average $F_{T_a} \geq a$, for several values of $a$.
As a comparison, it also displays the average number of such fluctuations in a control timeseries of duration $C_{gktl}$, divided in $N_c = C_{gktl} / T_a$ events.
This number is computed based on the assumption that the \ac{pdf} describing the random variable $F_T$ with $T=10\tau_c$ is Gaussian.
This hypothesis is motivated by figure~\ref{fig:pdf_averared} (\textbf{figure manquante}).
While this assumption does not hold for $F_T \geq 4\sigma_T$, it may still provide numbers relevant to the comparison with the algorithm.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{typical_drag_signal/typical_drag_signal.png}
  \caption{Typical temporal evolution of the drag acting on the square cylinder pictured in figure~\ref{fig:computational_domain}. The correlation time $\tau_c$ is defined further in this text and correspond to the typical fluctuation timescale of the drag.}
  \label{fig:typical_drag_signal}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{ecoulement_typique/ecoulement_typique.png}
  \caption{Vorticity dynamics corresponding to typical drag fluctuations over one correlation time unit $\tau_c$. Negative vorticity is generated along the bottom boundary, and advected away from the the obstacle by the mean flow.}
  \label{fig:typical_drag_signal}
\end{figure}

@@

% Malgré les limitations, c'est toujours mieux
% qu'un échantillonnage direct
Unsurprisingly, sampling larger fluctuations requires a larger population size, and therefore a larger computational cost.
Even though, table~\ref{tbl:nbTraj_tbl} shows that the \ac{gktl} algorithm is able to sample trajectories corresponding to values of the time-averaged drag that could
not be sampled through a direct sampling with equal computational cost.
Table~\ref{tbl:nbTraj_tbl} displays the number of trajectories that correspond to a time-average $F_{T_a} \geq a$, for several values of $a$.
As a comparison, it also displays the average number of such fluctuations in a control timeseries of duration $C_{gktl}$, divided in $N_c = C_{gktl} / T_a$ events.
This number is computed based on the assumption that the \ac{pdf} describing the random variable $F_T$ with $T=10\tau_c$ is Gaussian.
This hypothesis is motivated by figure~\ref{fig:PDF_AVG}.
While this assumption does not hold for $F_T \geq 4\sigma_T$, it may still provide numbers relevant to the comparison with the algorithm.
\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{PDF_AVG/PDF_AVG}
  \caption{PDF of average drag over $10\tau_c$}
  \label{fig:PDF_AVG}
\end{figure}
